---
title: "my-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(g11)
```


# Hi there, looking for some Regression Analysis?

[We got you.!](https://gabiitokazu.shinyapps.io/shiny_g11/)

**Package name:** `g11` (yes, no creativity!)
**GitHub repository:** [FinalProject-11](https://github.com/AU-R-Programming/FinalProject-11)   
**Published GitHub repository:** [FinalProject-11](https://github.com/gabiitokazu/desperation) 

This baby package is the implementation of the main basic functions that one would like to play around with Linear Regression. Yes! plots of residuals, F-test statistics, computation of the mean square prediction error.. P-value? Of course!.

Now, we had some problems getting the whole thing to run smoothly. So if you are Dr. Molinari and are interested on some good history, please check the [original repo](https://github.com/AU-R-Programming/FinalProject-11). You can find all the commits and the bumps and the erased code. But to see how the proper package is published, please go to [this repo](https://github.com/gabiitokazu/desperation), which shame on Gabi Itokazu, it is on her personal GitHub, BUT do not let yourself be fooled by it: this is a group authorship. Ha, talking about group, here are the authors:

* Eyoel Berhane
* John Mustapha
* Gabi Itokazu

#### Installation

Do you want to use it? Open that beautiful `RStudio` of your and type down

```
install.packages("devtools")
library(devtools)
devtools::install_github("gabiitokazu/desperation")
```

## Examples

```
install.packages("gamair")
library(gamair)
data(hubble)

x <- hubble$x
y <- hubble$y

# now try stuff:

g11_beta(y, x)
g11_ci(y, x, beta, alpha=0.01, method="bootstrap")
```



Hey. Have fun!


